---
title: "CHS_analysis"
author: "Chirvi M., Huber H.-P., Schneider C."
date: "07 2022"
output: html_document
---

### GENERAL SETTINGS

# (1) set working directory
```{r}

setwd("~/Projekte/Wealth Tax Misperception")
options(scipen = 999)

```

# (2) load all necessary libraries
```{r}

packages = c("quantreg", "ggplot2", "readr", 
             "dplyr", "scales", "devtools", 
             "gganimate", "gifski", "transformr",
             "tidyverse","magick", "readxl", 
             "ggpubr", "plm", "gplots", 
             "tseries", "lmtest", "clubSandwich", 
             "lme4", "apsrtable", "broom",
             "haven", "weights", "stargazer", 
             "sjPlot", "censReg", "reshape2")

lapply(packages, require, character.only = TRUE)

```


### LOAD DATA

```{r}

# read survey data (provided in gibtub)
data = readRDS("Data/CHS_data.rds")

# read ALLBUS data (https://doi.org/10.4232/1.13250) (need to register to dwownload data at GESIS)
allbus = read_dta("Data/ALLBUS_2018.dta")

# read topic calssifications
text = read_excel("Data/CHS_topics.xlsx")

```

### DATA PREPARATION

# (1) define treatment group variable
```{r}

data$treat = ifelse(!is.na(data$taxallowance_y_c), 1,
                    ifelse(!is.na(data$taxallowance_y_t), 2,
                           ifelse(!is.na(data$taxallowance_o_c), 3,
                                  ifelse(!is.na(data$taxallowance_o_t), 4, 0))))

```

# (2) define information/taxtaype treatment groups
```{r}

data$info = ifelse(data$treat == 2 | data$treat == 4, 1, 0)
data$taxtype = ifelse(data$treat == 1 | data$treat == 2, 1, 0)

```

# (3) define control variables
```{r}

data$control = (data$controltax1 + data$controltax2 + data$controlgrowth)/3
data$controltax = (data$controltax1 + data$controltax2)/2

```

# (4) define further variables
```{r}

data$children = ifelse(is.na(data$numberofchildren), NA,
                       ifelse(data$numberofchildren > 1, 1, 0))

data$employed = ifelse(is.na(data$employment), NA, 
                       ifelse(data$employment == 1 | data$employment == 2 | data$employment == 3, 1, 0))

data$university = ifelse(is.na(data$education), NA,
                         ifelse(data$education > 4, 1, 0))

data$married = ifelse(is.na(data$familystatus), NA,
                      ifelse(data$familystatus == 2, 1, 0))

data$highincome = ifelse(is.na(data$income), NA,
                         ifelse(data$income > 3, 1, 0))

data$leftparties = ifelse(is.na(data$party), NA,
                          ifelse(data$party == 4 | data$party == 5 | data$party == 6, 1, 0))

```

# (5) calculating effective tax rates
```{r}

ev_notax1 = 350000
ev_notax2 = 3000000
ev_notax3 = 10800000

data$taxrate1 = ifelse(!is.na(data$taxrate1_y_c), data$taxrate1_y_c/100,
                    ifelse(!is.na(data$taxrate1_y_t), data$taxrate1_y_t/100,
                           ifelse(!is.na(data$taxrate1_o_c), data$taxrate1_o_c/100,
                                  ifelse(!is.na(data$taxrate1_o_t), data$taxrate1_o_t/100,NA))))

data$taxrate2 = ifelse(!is.na(data$taxrate2_y_c), data$taxrate2_y_c/100,
                    ifelse(!is.na(data$taxrate2_y_t), data$taxrate2_y_t/100,
                           ifelse(!is.na(data$taxrate2_o_c), data$taxrate2_o_c/100,
                                  ifelse(!is.na(data$taxrate2_o_t), data$taxrate2_o_t/100,NA))))

data$taxrate3 = ifelse(!is.na(data$taxrate3_y_c), data$taxrate3_y_c/100,
                    ifelse(!is.na(data$taxrate3_y_t), data$taxrate3_y_t/100,
                           ifelse(!is.na(data$taxrate3_o_c), data$taxrate3_o_c/100,
                                  ifelse(!is.na(data$taxrate3_o_t), data$taxrate3_o_t/100,NA))))

data$taxallowance = ifelse(!is.na(data$taxallowance_y_c), data$taxallowance_y_c,
                        ifelse(!is.na(data$taxallowance_y_t), data$taxallowance_y_t,
                               ifelse(!is.na(data$taxallowance_o_c), data$taxallowance_o_c,
                                      ifelse(!is.na(data$taxallowance_o_t), data$taxallowance_o_t,NA))))


data$ev_ti1 = ifelse(data$treat == 3 | data$treat == 4, 
                     ev_notax1 - pmax((ev_notax1 - data$taxallowance)*data$taxrate1,0), NA)

data$ev_ti2 = ifelse(data$treat == 3 | data$treat == 4, 
                     ev_notax2 - pmax((ev_notax2 - data$taxallowance)*data$taxrate2,0), NA)

data$ev_ti3 = ifelse(data$treat == 3 | data$treat == 4, 
                     ev_notax3 - pmax((ev_notax3 - data$taxallowance)*data$taxrate3,0), NA)


wealth = function(basis, growthbase, growthrate, taxrate, allowance){
  ev_ti = basis
    for (i in 0:49)
      ev_ti = (ev_ti + (growthrate*basis*(growthbase^(i))) - pmax(taxrate*((ev_ti + (growthrate*basis*(growthbase^(i)))) - allowance),0))
    return(ev_ti)
}

data$ev_ti1 = ifelse(data$treat == 1 | data$treat == 2,
                     wealth(130000, 1.02000545373, 0.02000545373, data$taxrate1, data$taxallowance)
                     ,data$ev_ti1)

data$ev_ti2 = ifelse(data$treat == 1 | data$treat == 2,
                     wealth(1100000, 1.0202687185694, 0.0202687185694, data$taxrate2, data$taxallowance)
                     ,data$ev_ti2)

data$ev_ti3 = ifelse(data$treat == 1 | data$treat == 2,
                     wealth(4000000, 1.0200636583136851, 0.0200636583136851, data$taxrate3, data$taxallowance)
                     ,data$ev_ti3)

data$tr_eff1 = 1 - data$ev_ti1/ev_notax1
data$tr_eff2 = 1 - data$ev_ti2/ev_notax2
data$tr_eff3 = 1 - data$ev_ti3/ev_notax3

data$tr_eff1 = ifelse(data$taxrate1 == 0 | data$tr_eff1 < 0 | data$taxallowance >= 350000, 0, data$tr_eff1)
data$tr_eff2 = ifelse(data$taxrate2 == 0 | data$tr_eff2 < 0 | data$taxallowance >= 3000000, 0, data$tr_eff2)
data$tr_eff3 = ifelse(data$taxrate3 == 0 | data$tr_eff3 < 0 | data$taxallowance >= 10800000, 0, data$tr_eff3)

data$tr_eff = (data$tr_eff1 + data$tr_eff2 + data$tr_eff3)/3

```


### DATA CLEANING (Table 1)

```{r}

# delete incomplete tax rates
data = data %>%
  filter(!is.na(data$taxrate1) & !is.na(data$taxrate2) & !is.na(data$taxrate3))

# delete incoherent tax allowances
data = data %>%
  mutate(nonsense = ifelse(taxallowance %% 1000 == 0, 0, ifelse(taxallowance == 0, 0, ifelse(data$taxallowance > 10000, 0, 1)))) %>%
  filter(nonsense == 0)

```


### CREATE PANEL DATA

```{r}

# create a panel (long) for all effective tax rates (etr)
data_long_etr = gather(data, person, etr, tr_eff1:tr_eff3, factor_key = TRUE)

# create a panel (long) for all tax rates (tr)
data_long_tr = gather(data, person, tr, taxrate1:taxrate3, factor_key = TRUE)

```


### TREATMENT GROUPS

# (1) summary statistics of main variables [Table 2]
```{r}

# Age
tapply(data$age, data$treat, summary)

# Female
tapply(data$female, data$treat, summary)

# Married
tapply(data$married, data$treat, summary)

# Income
data %>%
  select(treat, income) %>%
  group_by(treat, income) %>%
  dplyr::summarise(Frequency = n()) %>% 
  mutate(Rel.Frequency = Frequency/sum(Frequency))

# Children
tapply(data$children, data$treat, summary)

# University
tapply(data$university, data$treat, summary)

# Employed
tapply(data$employed, data$treat, summary)

```

# (2) check whether sample is representative with respect to these variables [Table 2]
```{r}

# age
allbus$age = ifelse(allbus$age == -32, NA, allbus$age)
weighted.mean(allbus$age, allbus$wghtpew, na.rm = T)

wtd.t.test(data[data$treat == 1,]$age, allbus$age, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$age, allbus$age, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$age, allbus$age, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$age, allbus$age, weighty = allbus$wghtpew)

# female
allbus$female = ifelse(allbus$sex == 2, 1, 0)
weighted.mean(allbus$female, allbus$wghtpew)

wtd.t.test(data[data$treat == 1,]$female, allbus$female, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$female, allbus$female, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$female, allbus$female, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$female, allbus$female, weighty = allbus$wghtpew)

# married
allbus$married = ifelse(allbus$mstat == 1 | allbus$mstat == 2, 1, 0)
weighted.mean(allbus$married, allbus$wghtpew)

wtd.t.test(data[data$treat == 1,]$married, allbus$married, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$married, allbus$married, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$married, allbus$married, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$married, allbus$married, weighty = allbus$wghtpew)

# income
allbus$income = ifelse(allbus$incc <= 0, NA,
                        ifelse(allbus$incc <= 8, 1, 
                               ifelse(allbus$incc <= 14, 2, 
                                      ifelse(allbus$incc <= 18, 3,
                                             ifelse(allbus$incc <= 19,4 ,
                                                    ifelse(allbus$incc <= 20, 5, 6))))))

weighted.mean(allbus$income == 1, allbus$wghtpew, na.rm = T)
weighted.mean(allbus$income == 2, allbus$wghtpew, na.rm = T)
weighted.mean(allbus$income == 3, allbus$wghtpew, na.rm = T)
weighted.mean(allbus$income == 4, allbus$wghtpew, na.rm = T)
weighted.mean(allbus$income == 5, allbus$wghtpew, na.rm = T)
weighted.mean(allbus$income == 6, allbus$wghtpew, na.rm = T)

wtd.t.test(data[data$treat == 1,]$income == 1, allbus$income == 1, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 1,]$income == 2, allbus$income == 2, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 1,]$income == 3, allbus$income == 3, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 1,]$income == 4, allbus$income == 4, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 1,]$income == 5, allbus$income == 5, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 1,]$income == 6, allbus$income == 6, weighty = allbus$wghtpew)

wtd.t.test(data[data$treat == 2,]$income == 1, allbus$income == 1, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$income == 2, allbus$income == 2, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$income == 3, allbus$income == 3, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$income == 4, allbus$income == 4, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$income == 5, allbus$income == 5, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$income == 6, allbus$income == 6, weighty = allbus$wghtpew)

wtd.t.test(data[data$treat == 3,]$income == 1, allbus$income == 1, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$income == 2, allbus$income == 2, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$income == 3, allbus$income == 3, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$income == 4, allbus$income == 4, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$income == 5, allbus$income == 5, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$income == 6, allbus$income == 6, weighty = allbus$wghtpew)

wtd.t.test(data[data$treat == 4,]$income == 1, allbus$income == 1, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$income == 2, allbus$income == 2, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$income == 3, allbus$income == 3, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$income == 4, allbus$income == 4, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$income == 5, allbus$income == 5, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$income == 6, allbus$income == 6, weighty = allbus$wghtpew)

# children
allbus$children = ifelse(allbus$dk05 < 0 , NA, ifelse(allbus$dk05 == 3, 0, 1))
weighted.mean(allbus$children, allbus$wghtpew, na.rm = T)

wtd.t.test(data[data$treat == 1,]$children, allbus$children, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$children, allbus$children, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$children, allbus$children, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$children, allbus$children, weighty = allbus$wghtpew)

# university
allbus$university = ifelse(allbus$de15 < 0 , NA, ifelse(allbus$de15 == 1, 1, 0))
weighted.mean(allbus$university, allbus$wghtpew, na.rm = T)

wtd.t.test(data[data$treat == 1,]$university, allbus$university, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$university, allbus$university, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$university, allbus$university, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$university, allbus$university, weighty = allbus$wghtpew)

# employed
allbus$employed = ifelse(allbus$work == 4, 0, 1)
weighted.mean(allbus$employed, allbus$wghtpew, na.rm = T)

wtd.t.test(data[data$treat == 1,]$employed, allbus$employed, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 2,]$employed, allbus$employed, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 3,]$employed, allbus$employed, weighty = allbus$wghtpew)
wtd.t.test(data[data$treat == 4,]$employed, allbus$employed, weighty = allbus$wghtpew)

```

# (3) randomization check [Table C3]
````{r}

data$yearly = ifelse(data$treat == 1, 1, 0)
data$yearlyinfo = ifelse(data$treat == 2, 1, 0)
data$onetime = ifelse(data$treat == 3, 1, 0)
data$onetimeinfo = ifelse(data$treat == 4, 1, 0)

age1 = lm(yearly ~ age, data = data)
age2 = lm(yearlyinfo ~ age, data = data)
age3 = lm(onetime ~ age, data = data)
age4 = lm(onetimeinfo ~ age, data = data)
summary(age1)
summary(age2)
summary(age3)
summary(age4)

female1 = lm(yearly ~ female, data = data)
female2 = lm(yearlyinfo ~ female, data = data)
female3 = lm(onetime ~ female, data = data)
female4 = lm(onetimeinfo ~ female, data = data)
summary(female1)
summary(female2)
summary(female3)
summary(female4)

married1 = lm(yearly ~ married, data = data)
married2 = lm(yearlyinfo ~ married, data = data)
married3 = lm(onetime ~ married, data = data)
married4 = lm(onetimeinfo ~ married, data = data)
summary(married1)
summary(married2)
summary(married3)
summary(married4)

children1 = lm(yearly ~ children, data = data)
children2 = lm(yearlyinfo ~ children, data = data)
children3 = lm(onetime ~ children, data = data)
children4 = lm(onetimeinfo ~ children, data = data)
summary(children1)
summary(children2)
summary(children3)
summary(children4)

university1 = lm(yearly ~ university, data = data)
university2 = lm(yearlyinfo ~ university, data = data)
university3 = lm(onetime ~ university, data = data)
university4 = lm(onetimeinfo ~ university, data = data)
summary(university1)
summary(university2)
summary(university3)
summary(university4)

employed1 = lm(yearly ~ employed, data = data)
employed2 = lm(yearlyinfo ~ employed, data = data)
employed3 = lm(onetime ~ employed, data = data)
employed4 = lm(onetimeinfo ~ employed, data = data)
summary(employed1)
summary(employed2)
summary(employed3)
summary(employed4)

income1 = lm(yearly ~ factor(income), data = data)
income2 = lm(yearlyinfo ~ factor(income), data = data)
income3 = lm(onetime ~ factor(income), data = data)
income4 = lm(onetimeinfo ~ factor(income), data = data)

summary(income1)
summary(income2)
summary(income3)
summary(income4)

coeftest(income1, vcov = vcovHC(income1, type="HC1"))
coeftest(income2, vcov = vcovHC(income2, type="HC1"))
coeftest(income3, vcov = vcovHC(income3, type="HC1"))
coeftest(income4, vcov = vcovHC(income4, type="HC1"))

f1 = lm(yearly ~ age + female + married + factor(income) + children + university + employed, data = data)
f2 = lm(yearlyinfo ~ age + female + married + factor(income) + children + university + employed, data = data)
f3 = lm(onetime ~ age + female + married + factor(income) + children + university + employed, data = data)
f4 = lm(onetimeinfo ~ age + female + married + factor(income) + children + university + employed, data = data)

summary(f1)
summary(f2)
summary(f3)
summary(f4)

```


### REGRESSION ANALYSIS

# (1) Summary Statistics [Table B2]
```{r}

data %>%
  select(tr_eff, 
         age, 
         female, 
         inheritancetax, 
         futuretax, 
         pasttax, 
         leftparties, 
         redistribute, 
         inequality, 
         children, 
         university, 
         highincome, 
         employed, 
         control) %>%
  stargazer(as.data.frame(.), summary = TRUE, digits = 3, header = F)

```


# (2) Define Panel Data Frame
```{r}

# select relevant variables
data_long = data_long_etr %>%
  select(
    id,
    etr,
    info,
    taxtype,
    person,
    age,
    female,
    inheritancetax,
    futuretax,
    pasttax,
    leftparties,
    redistribute,
    inequality,
    children,
    university,
    highincome,
    employed,
    control
  )


# define pd dataframe
data_long = pdata.frame(data_long, index = c("id", "person"))

```

# (3) Baseline Regression Analysis [Table 3/B4]
```{r}

# random effects model without controls
random = plm(etr ~ info*taxtype 
                  + person, 
                  data = data_long, 
                  model = "random")



# random effects model with controls
random_C = plm(etr ~ info*taxtype 
                  + person
                  + age
                  + female
                  + inheritancetax
                  + futuretax
                  + pasttax
                  + leftparties
                  + redistribute
                  + inequality
                  + children
                  + university
                  + highincome
                  + employed
                  + control, 
                  data = data_long, 
                  model = "random")

# censored random effects model (tobit) without controls
tobit = censReg(etr ~ info*taxtype  
                  + person, 
                  data = data_long, 
                  method = "BHHH", 
                  nGHQ = 32)

# censored random effects model (tobit) with controls
tobit_C = censReg(etr ~ info*taxtype  
                  + person
                  + age
                  + female
                  + inheritancetax
                  + futuretax
                  + pasttax
                  + leftparties
                  + redistribute
                  + inequality
                  + children
                  + university
                  + highincome
                  + employed
                  + control, 
                  data = data_long, 
                  method = "BHHH", 
                  nGHQ = 32)

# create latex table
stargazer(random, random_C, tobit, tobit_C, header = F)

```

# (4) Heterogeneity Analysis [Table B5]
```{r}

# yearly wealth tax: random effects model with interactions
random_yearly_inter = plm(etr ~ info 
                  + person*info
                  + age*info
                  + female*info
                  + inheritancetax*info
                  + futuretax*info
                  + pasttax*info
                  + leftparties*info
                  + redistribute*info
                  + inequality*info
                  + children*info
                  + university*info
                  + highincome*info
                  + employed*info
                  + control*info, 
                  data = data_long[data_long$taxtype == 1,], 
                  model = "random")


# yearly wealth tax: censored random effects model (tobit) with interactions
tobit_yearly_inter = censReg(etr ~ info  
                  + person*info
                  + age*info
                  + female*info
                  + inheritancetax*info
                  + futuretax*info
                  + pasttax*info
                  + leftparties*info
                  + redistribute*info
                  + inequality*info
                  + children*info
                  + university*info
                  + highincome*info
                  + employed*info
                  + control*info,  
                  data = data_long[data_long$taxtype == 1,],  
                  method = "BHHH", 
                  nGHQ = 32)


# create latex table
stargazer(random_yearly_inter, tobit_yearly_inter, header = F)

```

# (5) Logitic Regression [Table 4/B6]
```{r}

# filter data set
data_within = data %>%
  filter(choice != 3) %>%
  mutate(dummy_yearly = as.factor(ifelse(choice == 2, 1, 0))) %>%
  mutate(taxamount = as.numeric(gsub("[[:punct:]]", "", total_within_o))/1000000) %>%
  mutate(taxquartile = as.factor(ntile(total_within_o, 4))) 

# logit model
logit1 = glm(dummy_yearly ~ 
                         + info
                         + taxtype*info
             ,family = binomial(link ='logit'),data = data_within)

logit1_C = glm(dummy_yearly ~ 
                         + info
                         + taxtype*info
                         + age 
                         + female 
                         + inheritancetax 
                         + futuretax 
                         + pasttax 
                         + leftparties
                         + redistribute 
                         + inequality 
                         + children 
                         + university
                         + highincome
                         + control 
                         + employed
             ,family = binomial(link ='logit'),data = data_within)

logit2 = glm(dummy_yearly ~ 
                         + info
                         + taxtype*info
                         + taxamount
             ,family = binomial(link ='logit'),data = data_within)

logit2_C = glm(dummy_yearly ~ 
                         + info
                         + taxtype*info
                         + taxamount
                         + age 
                         + female 
                         + inheritancetax 
                         + futuretax 
                         + pasttax 
                         + leftparties
                         + redistribute 
                         + inequality 
                         + children 
                         + university
                         + highincome
                         + control 
                         + employed
             ,family = binomial(link ='logit'),data = data_within)

# create latex table
stargazer(logit1, logit1_C, logit2, logit2_C , header = F)


```

### FIGURES

# (1) Figure 3: Baseline Results 
```{r}

df = data %>% 
  group_by(taxtype, info) %>% 
  summarise(n = n(), mean = mean(tr_eff), sd = sd(tr_eff)) %>%
  mutate(se=sd/sqrt(n))  %>%
  mutate(ic=se * qt((1-0.05)/2 + .5, n-1))

df$taxtype = ifelse(df$taxtype == 1, 0, 1)

df$taxtype = as.factor(df$taxtype)
levels(df$taxtype) = c("Yearly Wealth Tax","One-Time Wealth Tax")

df$info = as.factor(df$info)
levels(df$info) = c("Control","Treatment")

avg = c("Ø Wealth Levels", "Ø Wealth Levels", "Ø Wealth Levels", "Ø Wealth Levels")
df$avg = avg

ggplot(df, aes(x = avg, mean ,fill = factor(info))) +
  geom_bar(position = "dodge", stat = "summary", color = "black") +
  geom_errorbar(aes(ymin=mean-ic, ymax=mean+ic), width=.2,
                position=position_dodge(.9), size = 0.5) +
  scale_y_continuous(labels=function(x) format(scales::percent(x, accuracy = 1, suffix ="%")), 
                     breaks = c(0,0.1,0.2,0.3,0.4,0.5,0.6), 
                     limits = c(0,0.6)) +
  facet_grid(.~taxtype) +
  scale_fill_manual(name = "", values = c("#c1e7ff", "#004c6d")) +
  ylab("Effective Tax Rate") +
  xlab("") +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", legend.background = element_rect(fill=NA,
                                  size=0.5, linetype="solid", 
                                  colour ="black"))

```

# (2) Figure 4: Tax Allowance
```{r}

data_long_tr$taxtype = ifelse(data_long_tr$taxtype == 1, 0, 1)

data_long_tr$taxtype = as.factor(data_long_tr$taxtype)
levels(data_long_tr$taxtype) = c("Yearly Wealth Tax","One-Time Wealth Tax")

data_long_tr$info = as.factor(data_long_tr$info)
levels(data_long_tr$info) = c("Control","Treatment")

ggplot(data_long_tr, aes(taxallowance, color = factor(info), fill = factor(info))) +
geom_density(size = 1.5, alpha = 0.5, adjust = 1) +
  facet_grid(. ~ taxtype) +
  scale_color_manual(values = c("Control" = "#c1e7ff", "Treatment" = "#004c6d"), name = "") +
  scale_fill_manual(values = c("Control" = "#c1e7ff", "Treatment" = "NA"), name = "") +
  scale_x_continuous(labels=comma_format(prefix = "€"), limits = c(0, 1100000), breaks = c(0, 250000, 500000, 750000, 1000000)) +
  xlab("Tax Allowance") +
  ylab("Density") +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", legend.background = element_rect(fill=NA,
                                  size=0.5, linetype="solid", 
                                  colour ="black"))

```

# (4) Figure 5: Nominal Tax Rates
```{r}

#data_long_tr$taxtype = ifelse(data_long_tr$taxtype == 0, 1, 0)

#data_long_tr$taxtype = as.factor(data_long_tr$taxtype)
#levels(data_long_tr$taxtype) = c("Yearly Wealth Tax","One-Time Wealth Tax")

#data_long_tr$info = as.factor(data_long_tr$info)
#levels(data_long_tr$info) = c("Control","Treatment")

data_long_tr$person = as.factor(data_long_tr$person)
levels(data_long_tr$person) = c("€350,000", "€3,000,000", "€10,800,000")

data_long_tr$taxallowance_log = log(data_long_tr$taxallowance)

ggplot(data_long_tr, aes(tr, color = factor(info), fill = factor(info))) +
geom_density(size = 1.5, alpha = 0.5, adjust = 1)+
  facet_grid(person ~ taxtype, scales = "free") +
  scale_color_manual(values = c("Control" = "#c1e7ff", "Treatment" = "#004c6d"), name = "") +
  scale_fill_manual(values = c("Control" = "#c1e7ff", "Treatment" = "NA"), name = "") +
  scale_x_continuous(labels=function(x) format(scales::percent(x, accuracy = 1, suffix ="%")), limits = c(-0.01,1.01)) +
  xlab("Nominal Tax Rates") +
  ylab("Density") +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", legend.background = element_rect(fill=NA,
                                  size=0.5, linetype="solid", 
                                  colour ="black"))


```

# (5) Figure 6: Whithin Choice.
```{r}

df = data %>%
  group_by(taxtype, info, choice) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

df$taxtype = as.factor(df$taxtype)
levels(df$taxtype) = c("One-Time Wealth Tax", "Yearly Wealth Tax")
df$taxtype = factor(df$taxtype, levels = c("Yearly Wealth Tax","One-Time Wealth Tax"))

df$info = as.factor(df$info)
levels(df$info) = c("Control","Treatment")

df$choice = as.factor(df$choice)
levels(df$choice) = c("One-Time Wealth Tax","Yearly Wealth Tax", "No Preference")
df$choice = factor(df$choice, levels = c("Yearly Wealth Tax", "One-Time Wealth Tax", "No Preference"))

ggplot(df, aes(factor(info), freq, fill = factor(choice))) + 
  geom_bar(position = "dodge", stat = "summary", color = "black") +
  facet_grid(. ~ taxtype) +
  scale_y_continuous(labels=function(x) format(scales::percent(x, accuracy = 1, suffix ="%")), 
                    breaks = c(0,0.25, 0.5, 0.75), 
                    limits = c(0,0.8)) +
  scale_x_discrete(label = c("Control", "Treatment")) +
  scale_fill_manual(values = c("Yearly Wealth Tax" = "#004c6d", "One-Time Wealth Tax" = "#c1e7ff", "No Preference" = "#999999"), name = "") +
  ylab("Share") +
  xlab("") +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", legend.background = element_rect(fill=NA,
                                  size=0.5, linetype="solid", 
                                  colour ="black"))

```

# (6) Figure 6: Reasoning
```{r}

reasons = inner_join(data_within[,c("id", "choice")], text, by = "id")

df = reasons %>% 
  group_by(choice) %>%
  summarise(t1 = mean(topic1),
            t2 = mean(topic2),
            t3 = mean(topic3),
            t4 = mean(topic4),
            t5 = mean(topic5),
            t6 = mean(topic6),
            t7 = mean(topic7),
            t8 = mean(topic8),
            t9 = mean(topic9),
            t10 = mean(topic10),
            t11 = mean(topic11),
            t12 = mean(topic12),
            tn = mean(topicnone)) %>%
  select(-tn)

meltdf = melt(df, id.vars = "choice")

meltdf$choice = as.factor(meltdf$choice)
levels(meltdf$choice) = c("One-Time Wealth Tax", "Yearly Wealth Tax")
meltdf$choice = factor(meltdf$choice, levels = c("Yearly Wealth Tax", "One-Time Wealth Tax"))

ggplot(meltdf, aes(x = reorder(variable, value), y= value, fill = factor(choice))) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  coord_flip() +
  #facet_grid(. ~ choice, scales = "free") +
  #scale_color_manual(values = c("Control" = "#c1e7ff", "Treatment" = "#004c6d"), name = "") +
  scale_fill_manual(values = c("Yearly Wealth Tax" = "#004c6d", "One-Time Wealth Tax" = "#c1e7ff"), name = "") +
  scale_y_continuous(labels=function(x) format(scales::percent(x, accuracy = 1, suffix ="%")), limits = c(0,0.4)) +
  scale_x_discrete(labels = c(
                              "Wealth taxes generally rejected",
                              "Tax burden equivalent",
                              "Taxes restrict economy",
                              "Early demise is possible",
                              "Fairer taxation",
                              "Prevention of tax avoidance",
                              "One big payment is less effort",                              
                              "Assets could decrease unexpectedly",
                              "Similar to inheritance tax/heirs are burdened",
                              "Financial freedom during life",
                              "Smaller amounts easier to manage",
                              "Continuous and predictable tax revenue")) +
  xlab("Reasons") +
  ylab("Share") +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", legend.background = element_rect(fill=NA,
                                  size=0.5, linetype="solid", 
                                  colour ="black"))


```

# (5) Figure C1: Round Number Bias
```{r}

data_long_tr$taxtype = ifelse(data_long_tr$taxtype == 0, 1, 0)

data_long_tr$taxtype = as.factor(data_long_tr$taxtype)
levels(data_long_tr$taxtype) = c("Yearly Wealth Tax","One-Time Wealth Tax")

data_long_tr$info = as.factor(data_long_tr$info)
levels(data_long_tr$info) = c("Control","Treatment")

data_long_tr$person = as.factor(data_long_tr$person)
levels(data_long_tr$person) = c("€350,000", "€3,000,000", "€10,800,000")

ggplot(data_long_tr[data_long_tr$tr <= 0.03 & data_long_tr$taxtype == "Yearly Wealth Tax",], aes(x = tr, fill = factor(info))) +
geom_bar(aes(y=..count..), stat = "bin", binwidth = 0.001,  position = "dodge", color = "black") + 
scale_fill_manual(values = c("Control" = "#c1e7ff", "Treatment" = "#004c6d"), name = "") +
scale_x_continuous(labels=function(x) format(scales::percent(x, accuracy = 1, suffix ="%"))) +
xlab("Nominal Tax Rates") +
ylab("Count") +
  theme_bw(base_size = 28) +
  theme(legend.position = "bottom", legend.background = element_rect(fill=NA,
                                  size=0.5, linetype="solid", 
                                  colour ="black"))


```
